Learning constraints in tabular data

### 2016-05-13 Paper/ECAI/tabular.tex
Corrected algorithm
Cosmetic

\begin{algorithm}[t]
  \begin{algorithmic}
    \footnotesize
    \State \textbf{Input:} $\groups$ -- groups, $\constraints$ -- \template's, \dependencies -- dependency graph
    \State \textbf{Output:} $C$ -- learned constraints
    \State $C \gets \emptyset$ %\Comment{The set of constraints}
  \ForAll{$t \in \constrainttorder(\constraints,\dependencies)$}
  \State $n \gets$ number of arguments of constraint $c_t$
    \ForAll{$(G_1, \dots, G_n) \in \generategroups(t, \groups, C)$}
      \State $C \gets C \cup \findassignment(t, (G_1, \dots, G_n))$
    \EndFor
  \EndFor\\
\Return $C$
\end{algorithmic}
\caption{Tabular constraint learning}
\label{algo:tcl}
\end{algorithm}

@@

The $\constrainttorder(\constraints,\dependencies)$ module in our method takes a set of {\template}s and a DAG as input and produces a linear ordering of the templates such that the more general, implied constraint templates (the requirements) are ordered before the templates that depend on them.

>>>>

\begin{algorithm}[t]
  \begin{algorithmic}
    \footnotesize
    \State \textbf{Input:} $\groups$ -- groups, $\constraints$ -- \template's, \dependencies -- dependency graph
    \State \textbf{Output:} $C$ -- learned constraints
    \State $C \gets \emptyset$ %\Comment{The set of constraints}
  \ForAll{$s \in \constrainttorder(\constraints,\dependencies)$}
  \State $n \gets$ number of arguments of template $s$
    \ForAll{$(G_1, \dots, G_n) \in \generategroups(s, \groups, C)$}
      \State $C \gets C \cup \findassignment(s, (G_1, \dots, G_n))$
    \EndFor
  \EndFor\\
\Return $C$
\end{algorithmic}
\caption{Tabular constraint learning}
\label{algo:tcl}
\end{algorithm}

@@

The $\constrainttorder(\constraints,\dependencies)$ module in our method takes a set of {\template}s~(\constraints) and a DAG~(\dependencies) as input and produces a linear ordering of the templates such that the more general, implied constraint templates (the requirements) are ordered before the templates that depend on them.
